Management frequency and extinction risk

### 2018-05-04 notebook/ms/SI6.Rmd
More start to the sixth SI

>>>>

For a single simulation, the `gmse_table` function prints out key information from a `gmse` simulation result. The example provided in the GMSE documentation is below.

```{r}
gmse_sim  <- gmse(time_max = 10, plotting = FALSE);
sim_table <- gmse_table(gmse_sim = gmse_sim);
print(sim_table)
```

We can also only record the last time step in `gmse_table`.

```{r}
sim_table_last <- gmse_table(gmse_sim = gmse_sim, all_time = FALSE);
print(sim_table_last)
```

The `gmse_replicates` function replicates multiple simulations under the same initial conditions, then returns a table showing the values of all simulations. This can be useful, for example, for testing how often a population is expected to go to extinction or carrying capacity under a given set of parameter values.
